Possibilistic evaluation of fuzzy temporal intervals

### 2011-12-01 estylf2012/estylf2012_en.tex
Update for the estylf paper.

There are several proposals in the literature for inferring uncertainty about sets from uncertainty about values. It is of particular interest for fuzzy temporal databases, the application on temporal intervals. The transformation from two ill-known temporal points to a ill-known set has been discussed in \cite{Garrido2009}. In this work we will analyze the major pitfalls of these approaches and the benefit of using the mechanism proposed in \cite{Pon11}.

@@

\section{\label{sec:preliminaries}PRELIMINARIES}
In this section we will introduce some basic concepts. First of all, an introduction to possibility theory is explained. Then, the concepts of fuzzy numbers and fuzzy intervals introduced by Dubois and Prade \cite{Dubois1983} are discussed. Finally, a brief introduction to temporal databases is done.

@@

In this example it is shown how this transformation is misleading: it is clear that the temporal interval $[3,6]$ is completely contained by the fuzzy temporal interval represented by $[X,Y]$. Nevertheless, the \emph{CONTAINS} operator applied to this transformation returns a 0.667 membership degree. Therefore, if the user is looking for a temporal interval $[a,b]$ and the database contains a tuple with a fuzzy interval $[X,Y]$, this transformation returns a possibility below 1, thus the user may interprete that the temporal interval $[a,b]$ is not completely inside the fuzzy interval $[X,Y]$. Plus, there is not possible to compute a necessity measure for the \emph{CONTAINS} operator in order to obtain more information about $[a,b]$.

@@

This transformation is also misleading. Even though the possibility obtained is similar to the possibility obtained in our proposal, there is not possible to compute the necessity for the \emph{CONTAINS} operator. Therefore, it is not possible to obtain a complete information for the interval $[a,b]$ w.r.t the fuzzy interval $[X,Y]$.

@@

\section{\label{sec:conclusions}CONCLUSIONS AND FUTURE WORK}
The problem of evaluation of sets in the framework of possibility theory has been addressed by Dubois and Prade. They conclude that a correct treatment of sets imply an overly complex possibility distribution. Based on the previous work from the authors, this work is focused on the evaluation of fuzzy temporal interval in the framework of possibility theory. The aim of the paper is to clarify the difference between fuzzy numbers, fuzzy intervals and ill-known intervals. Several proposals can be found in the literature with respect to transforming two fuzzy numbers into a fuzzy interval. We have shown that these techniques are not fully correct in the sense of possibility theory.\\

>>>>

%There are several proposals in the literature for inferring uncertainty about sets from uncertainty about values. It is of particular interest for fuzzy temporal databases, the application on temporal intervals. 
The transformation from two ill-known temporal points to an ill-known set has been discussed in \cite{Garrido2009}. In this work we will analyze the major pitfalls of these approaches and the benefit of using the mechanism proposed in \cite{Pon11}.

@@

\section{\label{sec:preliminaries}PRELIMINARIES}
In this section we will introduce some basic concepts. First of all, an introduction to possibility theory is included. Then, the concepts of fuzzy numbers and fuzzy intervals introduced by Dubois and Prade \cite{Dubois1983} are discussed. Finally, a brief introduction to temporal databases is done.

@@

In this example it is shown how this transformation is misleading: it is clear that the temporal interval $[3,6]$ is completely contained by the fuzzy temporal interval represented by $[X,Y]$. Nevertheless, the \emph{CONTAINS} operator applied to this transformation returns a 0.667 membership degree. Therefore, if the user is looking for a temporal interval $[a,b]$ and the database contains a tuple with a fuzzy interval $[X,Y]$, this transformation returns a possibility below 1, thus the user may interpret that the temporal interval $[a,b]$ is not completely inside the fuzzy interval $[X,Y]$. Plus, it is not possible to compute a necessity measure for the \emph{CONTAINS} operator in order to obtain more information about $[a,b]$.

@@

This transformation is also misleading. Even though the possibility obtained is similar to the possibility obtained in our proposal, it is not possible to compute the necessity for the \emph{CONTAINS} operator. Therefore, it is not possible to obtain a complete information for the interval $[a,b]$ w.r.t the fuzzy interval $[X,Y]$.

@@

\section{\label{sec:conclusions}CONCLUSIONS AND FUTURE WORK}
In this work we have presented a framework to deal with the evaluation for the ill-known interval $[X,Y]$ to contain the crisp interval $[a,b]$. Our proposal keeps the reasoning in the power set $\Pow(U)$ while the transformations make the reasoning in the set $U$, therefore the transformations result in a possibilistic information lost. The proposed framework offer more accurate results, as shown in the examples. Also the two measures provided: possibility and necessity can be used for the ranking of results.The framework will be extended with the implementation of the Allen's operators and the comparison between two ill-known intervals.
%
%
%The problem of evaluation of sets in the framework of possibility theory has been addressed by Dubois and Prade. They conclude that a correct treatment of sets imply an overly complex possibility distribution. Based on the previous work from the authors, this work is focused on the evaluation of fuzzy temporal interval in the framework of possibility theory. 
%
%
%
%The aim of the paper is to clarify the difference between fuzzy numbers, fuzzy intervals and ill-known intervals. Several proposals can be found in the literature with respect to transforming two fuzzy numbers into a fuzzy interval. We have shown that these techniques are not fully correct in the sense of possibility theory.\\
%
